Designing Efficient Smart Camera Networks For Public Saftey

### 2013-10-16 Paper/main.tex
added bandwidth section

%%Requirements for today's wireless Smart Camera Networks
\section{Smart Camera Surveillance}
Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes in public spaces. To
understand how these state of the art systems are improving on designs of the past one must define what makes these surveillance systems "smart". These
smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue of network resource
utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment scenarios. Then in
almost every application considering power consumption of each node is very important if one is give an analysis of the systems efficiency. If these
systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also ensuring that the data recorded
is actually quality information that could be used by officials. \\

\section{Wireless Smart Camera Networks Taxonomy}
\-- Purpose criteria for classification of wireless Smart camera networks \\ \\
\-- A comparison chart of different hardware components of their systems 
	being used\\ \\
\-- A comparison chart of software design features (computer vision, network
	topologies, bandwidth/energy saving techniques, etc. )\\ \\
\-- Explain each classification criterion, provide examples, etc.\\ \\

@@

\section{Conclusion}
\-- tie up paper
~\cite{DSPcam}
~\cite{HuSIMS}
~\cite{Citric}
~\cite{OmniEye}
~\cite{ScoutNode}
~\cite{SensEye}
~\cite{WiFLIP}

>>>>

%%Requirements for today's wireless Smart Camera Networks

\section{Smart Camera Surveillance}
Researchers and Commercial companies are designing wireless smart camera networks in surveillance applications to prevent crimes in public spaces. To
understand how these state of the art systems are improving on designs of the past one must define what makes these surveillance systems "smart". These
smart camera network systems have common goals when it comes creating more efficient surveillance applications. First, the issue of network resource
utilization is an issue all systems need to consider if those surveillance systems are to be scalable in crowded wireless deployment scenarios. Then in
almost every application considering power consumption of each node is very important if one is give an analysis of the systems efficiency. If these
systems are to be monitoring public spaces the smart camera networks need to be keeping the data recorded secure and also ensuring that the data recorded
is actually quality information that could be used by officials. \\

%% Wireless Smart Camera Networks Taxonomy Divided into 3 sections
%% 1 Bandwidth efficieny 2 power consumption 3 Quality of data
\subsection{Bandwidth Efficiency}
Video data is rich with useful information that other sensor source can’t provide, however video data quickly becomes very large in size as time goes on.
Nodes competing for network connectivity while maintaining quality on live video feed can soon become a problem as the network grows or if other nodes
not in the system share the connection. One way to combat this is by assuring the data recorded is useful and actually recording video data that can be
used to do detection of events. A common technique is to use other non-image sensors to provide separate data that can be used to determine if the camera
should record video at all.

\-- A comparison chart of different hardware components of their systems 
	being used\\ \\
\-- A comparison chart of software design features (computer vision, network
	topologies, bandwidth/energy saving techniques, etc. )\\ \\
\-- Explain each classification criterion, provide examples, etc.\\ \\

\subsection{Lowering Power Consumption}

\subsection{Quality of data produced}

@@

\section{Lessons to take away}

\-- just so it compiles here are the references to be used:
~\cite{DSPcam}
~\cite{HuSIMS}
~\cite{Citric}
~\cite{OmniEye}
~\cite{ScoutNode}
~\cite{SensEye}
~\cite{WiFLIP}
